---
title: "Descriptive summary of Images in the database"
author: "Chandan Kumar Pandey"
output:
  word_document: default
  html_notebook: default
  pdf_document: default
  html_document:
    df_print: paged
---
### This report is the descriptive result of the tiger and leopard images in the database which we will be using for training the machine learning network. 


```{r loading the data in the file,warning=FALSE,echo=FALSE,comment=FALSE,message=FALSE}
Tiger<-read.csv("Animal_cature_details.csv",header = T)
Tiger$name<-rep("Tiger",nrow(Tiger))
leopard<-read.csv("leopard_capture_details.csv",header = T)
leopard$name<-rep("leopard",nrow(leopard))
require(dplyr)
require(ggplot2)
animal_data<-bind_rows(Tiger,leopard)
```

### Number of tigers and leopards in different capture mode.

The are total `r nrow(animal_data)` images belonging to `r length(unique(animal_data$id))` individuals taken in `r length(unique(animal_data$site))` different sites. Among these animals  there are `r nrow(Tiger)` images for `r length(unique(Tiger$id))` tigers and `r nrow(leopard)` images belonging to `r length(unique(leopard$id))` leopards.
However, the images in the database consist of camera traps, photo from naturalist, dead tigers, pelted skin etc. The following graph provide summary of this.


```{r CPMD, warning=F,echo=F,message=F}
require(ggplot2)
require(gridExtra)
library(tidyr)
CPMD<-group_by(animal_data[is.na(animal_data$CPMD)==F,],CPMD,name)%>%
  summarise(value=n(),indivi=n_distinct(id))%>%
  as.data.frame()
CPMD$CPMD<-ordered(CPMD$CPMD,levels=c("CT","PH","CP","DE","FD","PE","MV"))
spread_CPMD<-spread(CPMD[,-4],key = c("CPMD"),value = c("value"),fill = 0)
spread_CPMD$rest_all<-rowSums(spread_CPMD[,4:8])
spread_CPMD<-spread_CPMD[,c(1,2,3,9)]
CPMD_img<-spread_CPMD%>%pivot_longer(!name, names_to="CPMD",values_to="count")%>%as.data.frame()
CPMD_img$name<-ordered(CPMD_img$name,levels=c("Tiger","leopard"))
cmpd_plot<-ggplot(data = CPMD_img,aes(y=count,x=CPMD,fill=as.factor(name)))
number<-cmpd_plot+geom_bar(stat="identity",position =position_dodge(0.9) )+
  geom_text(aes(label=count),hjust=0.25,vjust=-1,size=3,position = position_dodge(0.9),angle=40)+
  ylim(c(0,28000))+
  labs(x="",y="Number of images",label="Species")+
  theme_classic()+
  scale_fill_manual(name="",values=c("Darkblue","green"),labels=c("Tiger","Leopard"))+
  scale_x_discrete(labels=c("Camera Trap Photos","Photos by Naturalists","Other Photos"))

#indviduals
spread_ind<-spread(CPMD[,-3],key = c("CPMD"),value = c("indivi"),fill = 0)
spread_ind$rest_all<-rowSums(spread_ind[,4:8])
spread_ind<-spread_ind[,c(1,2,3,9)]
CPMD_ind<-spread_ind%>%pivot_longer(!name, names_to="CPMD",values_to="count")%>%as.data.frame()
CPMD_ind$name<-ordered(CPMD_ind$name,levels=c("Tiger","leopard"))
cmpd_plot_ind<-ggplot(data = CPMD_ind,aes(y=count,x=CPMD,fill=as.factor(name)))
ind<-cmpd_plot_ind+geom_bar(stat="identity",position =position_dodge(0.9) )+
  geom_text(aes(label=count),hjust=0.25,vjust=-1,size=3,position = position_dodge(0.9),angle=40)+
  ylim(c(0,2000))+
  labs(x="",y="Number of individuals",label="")+
  theme_classic()+
  scale_fill_manual(name="",values=c("Darkblue","green"),labels=c("Tiger","Leopard"))+
  scale_x_discrete(labels=c("Camera Trap Photos","Photos by Naturalists","Other Photos"))
grid.arrange(number,ind,nrow=2)
```

### Histrogram of number of image per individuals. 

It is clear that **`r round(spread_CPMD[1,2]/rowSums(spread_CPMD[1,-1]),2)*100`%** leopards and **`r round(spread_CPMD[2,2]/rowSums(spread_CPMD[2,-1]),2)*100`%** Tigers images are from camera trap.  Therefore we will only be using the image that were capture using camera traps. 

```{r historgrams of number of images per ind,echo=FALSE,warning=FALSE,message=FALSE}
library(ggplot2)
#tiger
camera_trap_data_tiger<-Tiger[Tiger$CPMD=="CT",]
camera_trap_data_tiger<-camera_trap_data_tiger[is.na(camera_trap_data_tiger$CPMD)==F,]
ploting_hist_tiger<-group_by(camera_trap_data_tiger,id)%>%summarise(count=n())%>%as.data.frame()
ploting_hist_tiger<-ploting_hist_tiger[order(ploting_hist_tiger$count),]
ploting_hist_tiger$intervel<-c("<=10","11-20","21-30","31-40", "41-50", ">50")[
  findInterval(ploting_hist_tiger$count,c(0,11,21,31,41,51,Inf))
]
ploting_hist_tiger$intervel<-ordered(ploting_hist_tiger$intervel,levels=c("<=10","11-20","21-30","31-40", "41-50", ">50"))
final_plot_tiger<-group_by(ploting_hist_tiger,intervel)%>%summarise(count=n())%>%as.data.frame()
#leopard
camera_trap_data_leo<-leopard[leopard$CPMD=="CT",]
camera_trap_data_leo<-camera_trap_data_leo[is.na(camera_trap_data_leo$CPMD)==F,]
ploting_hist_leo<-group_by(camera_trap_data_leo,id)%>%summarise(count=n())%>%as.data.frame()
ploting_hist_leo<-ploting_hist_leo[order(ploting_hist_leo$count),]
ploting_hist_leo$intervel<-c("<=10","11-20","21-30","31-40", "41-50", ">50")[
  findInterval(ploting_hist_leo$count,c(0,11,21,31,41,51,Inf))
]
ploting_hist_leo$intervel<-ordered(ploting_hist_leo$intervel,levels=c("<=10","11-20","21-30","31-40", "41-50", ">50"))
final_plot_leo<-group_by(ploting_hist_leo,intervel)%>%summarise(count=n())%>%as.data.frame()
final_plot_leo$name<-rep("Leopard",nrow(final_plot_leo))
final_plot_tiger$name<-rep("Tiger",nrow(final_plot_tiger))
final_plot<-bind_rows(final_plot_leo,final_plot_tiger)
final_plot$name<-ordered(final_plot$name,levels=c("Tiger","Leopard"))
hist_p<-ggplot(data = final_plot,aes(y=count,x=intervel,fill=name))
hist_p+geom_bar(stat="identity",position = position_dodge(0.9))+labs(x="Number of Images per Individual",y="Number of Individuals")+theme_classic()+
  ylim(c(0,1200))+geom_text(aes(label=count),hjust=0.2,vjust=-1,size=2,position = position_dodge(0.9),angle=20)+
  theme(axis.text.x = element_text(size = 8))+
  scale_fill_manual(name="",values=c("Darkblue","green"),labels=c("Tiger","Leopard"))
```

Form the above graph it is clear that 1107 leopards  and 933 tigers have 10 or less number of images. Moreover over `r sum(final_plot$count[1:5])` out of `r sum(final_plot$count[1:6])` leopards and   `r sum(final_plot$count[7:11])` out of `r sum(final_plot$count[7:12])` tigers indivduals fall in the range of less that 50 images.  


### Number of camera trap images on different flanks

Further camera trap images are take in left and right flank. The number of left and right flanks might not be same for all the tigers. 

```{r flanks plot,echo=F,message=F,warning=F}
camera_trap_data<-bind_rows(camera_trap_data_leo,camera_trap_data_tiger)
camera_trap_data$side[grep("L",camera_trap_data$side)]<-"L"
camera_trap_data$side[grep("R",camera_trap_data$side)]<-"R"
flanks<-group_by(camera_trap_data,id,side,name)%>%summarise(number=n())%>%as.data.frame()

library(tidyr)
require(gridExtra)
flank_plot<-spread(data = flanks,key = "side",value = "number",fill = 0)
flank_plot<-flank_plot[,-5]
flank_plot<-flank_plot[is.na(flank_plot$name)==F,]
flank_plot$name<-stringr::str_replace(flank_plot$name,"leopard","Leopard")
flank_plot$name<-ordered(flank_plot$name,levels=c("Tiger","Leopard"))

spread_plot<-ggplot(data =  flank_plot,aes(x=log10(L),y=log10(R),color=name))
spread_plot+geom_point(shape=19,size=1.6)+labs(x="Number of left flank per individuals \n (in log scale base 10)",y="Number of right flank per individuals\n(in log base 10 scale)")+
  geom_abline(slope = 1, intercept = 0)+theme_classic()+scale_color_manual(values=c("Darkblue","green"),labels=c("Tiger","Leopard"),name="")

```
### Camera trap images at different times of the day

As from the discussion it was clear that night and day image was important in classification of the image. It is also important which training the network

```{r traing with time,echo=F,warning=F,message=F}
require(lubridate)
require(data.table)
camera_trap_data<-camera_trap_data[is.na(camera_trap_data$time_seen)==F,]
camera_trap_data$time_seen<-as_datetime(camera_trap_data$time_seen)

time_data<-as_datetime(camera_trap_data$time_seen,tz="GMT")
time_data<-format(time_data,format = "%H%M%S")
time_data<-time_data%>%na.omit()
Time_block=as.POSIXct(strptime(c("060000","180000"),"%H%M%S"),tz="GMT")
Time_block<-format(Time_block,format = "%H%M%S")
time_of_day<-case_when(
between(time_data,Time_block[1],Time_block[2]) ~"morning",
        TRUE ~"night")
Time_data_frame<-data.frame(time=time_data,class=time_of_day,name=camera_trap_data$name)
Bar_chart<-group_by(Time_data_frame,class,name)%>%summarise(count=n())%>%as.data.frame()
Bar_chart$name<-stringr::str_replace(Bar_chart$name,"leopard","Leopard")
Bar_chart$name<-ordered(Bar_chart$name,levels=c("Tiger","Leopard"))
barp<-ggplot(data = Bar_chart,aes(x=class,y=count,fill=name))
barp+geom_bar(stat = "identity",color="black",position = position_dodge(0.9))+
  theme_classic()+labs(x="",y="Number of Images")+
  scale_x_discrete(breaks=unique(Bar_chart$class),labels=c("Day-time (0600 - 1800 Hrs)","Night-time (1801 - 0559 Hrs)"))+
  geom_text(aes(label=count),hjust=0.2,vjust=-1,size=5,position = position_dodge(0.9),angle=20)+ylim(c(0,23000))+
  scale_fill_manual(name="",values = c("Darkblue","green"),labels=c("Tiger","Leopard"))
```
The discrpency in the total number of image in above graph and the first graps is due to fact that for some camera trap images the timing are missing. To be exact, there are `r nrow(animal_data[animal_data$CPMD=="CT",])-nrow(camera_trap_data)` camera trap images that do not have time associated with it


### Images and individual at diffrent sites
```{r diffrent sites, warning=F,echo=F,message=F}
## number of images 
require(dplyr)
camera_trap_data$name<-stringr::str_replace(camera_trap_data$name,"leopard","Leopard")
img_site<-group_by(camera_trap_data,site,name)%>%summarise(count=n(),disti_ind=n_distinct(id))%>%as.data.frame()
img_site<-na.omit(img_site)
img_site<-img_site[order(-img_site$count),]
img_site$site<-ordered(img_site$site,levels=unique(img_site$site))
img_site$name<-ordered(img_site$name,levels=c("Tiger","Leopard"))
plot_img<-ggplot(data = img_site,aes(x=site,y=count,fill=name))+geom_bar(stat = "identity",position = position_dodge(0.9))+theme_classic()+theme(axis.text.x = element_text(angle = 45,vjust = 0.5))+
  labs(x="Number of images",y="")+
  scale_fill_manual(name="",values=c("Darkblue","green"),labels=c("Tiger","Leopard"))
## number of individuals. 
plot_ind<-ggplot(data = img_site,aes(x=site,y=disti_ind,fill=name))+geom_bar(stat = "identity",position = position_dodge(0.9))+theme_classic()+theme(axis.text.x = element_text(angle = 45,vjust = 0.5))+
  labs(x="Number of individuals",y="")+
  scale_fill_manual(name="",values=c("Darkblue","green"),labels=c("Tiger","Leopard"))
gridExtra::grid.arrange(plot_img,ind_site,nrow=1,ncol=2)

library(knitr)
names(img_site)<-c("Camera trapsites","Speceis","number of images","number of individuals")
kable(img_site[img_site[,2]=="Tiger",],row.names = F,caption = "Tiger images")
kable(img_site[img_site[,2]=="Leopard",],row.names = F,caption = "Leopard images")

```
The final out come from the data is that most of the individuals have 1-10 pictures, while most of the images are from camera trap data.  



